Fractional Types

### 2019-10-31 fracGC/p.tex
a bit of reorg

\paragraph*{Temporary Storage using Ancilla Bits.} The universality of
the Toffoli gate for classical reversible computing and of the
combination of the Toffoli and Hadamard gates for quantum computing
should not distract from efficiency and safety concerns. The theorems
proving universality (i) assume that temporary storage (often called
\emph{ancilla bits}) may be used~\cite{Toffoli:1980}, and (ii) that
this temporary storage is returned to its initial state before
de-allocation. Indeed if no temporary storage is allowed, the Toffoli
gate is not universal~\cite{DBLP:conf/innovations/AaronsonGS17} and as
we demonstrate using space-time tradeoffs in Sec.~\ref{sec:examples},
the more temporary storage is allowed, the more efficient certain
computations could become. The condition requiring that the temporary
storage is only de-allocated when returned to its initial condition is
a safety condition. Violating this condition destroys the symmetry
between input and output making the circuits not reversible and, in
the quantum model, causes irreversible decoherence problems. As
reviewed in Sec.~\ref{sec:examples}, ancilla have a number of critical
applications and yet are poorly supported in current reversible and
quantum programming languages making them a common source of bugs.

@@

@@

Toffoli4 using 2 Toffoli3: core of proof of universality; simple
enough

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Extra for now}

@@

Reversible/Quantum Circuits and Ancilla Wires: Early use of ancillas
in Toffoli's paper to implement arbitrary reversible functions using a
fixed number of 3 input gates
\url{https://link.springer.com/content/pdf/10.1007%2F3-540-10003-2_104.pdf}

Use examples from Ricercar

@@

A Comonad for Pi:

@@

Denotations:

>>>>

\paragraph*{Temporary Storage using Ancilla Bits.} The universality of
the Toffoli gate for classical reversible computing and of the
combination of the Toffoli and Hadamard gates for quantum computing
should not distract from efficiency and safety concerns. The theorems
proving universality (i) assume that temporary storage (often called
\emph{ancilla bits}) may be used~\cite{Toffoli:1980}, and (ii) that
this temporary storage is returned to its initial state before
de-allocation. Indeed if no temporary storage is allowed, the Toffoli
gate is not universal~\cite{DBLP:conf/innovations/AaronsonGS17} and as
we demonstrate using space-time tradeoffs in Sec.~\ref{sec:examples},
the more temporary storage is allowed, the more efficient certain
computations could become. The condition requiring that the temporary
storage is only de-allocated when returned to its initial condition is
a safety condition. Violating this condition destroys the symmetry
between input and output making the circuits not reversible and, in
the quantum model, causes irreversible decoherence problems. As
reviewed in Sec.~\ref{sec:examples}, ancilla bits have a number of critical
applications and yet are poorly supported in current reversible and
quantum programming languages making them a common source of bugs.

@@

%%%
\subsection{Applications}

%%%
\subsection{Language Support}

@@

@@

%%%
\subsection{Examples}

Toffoli4 using 2 Toffoli3: core of proof of universality; simple
enough. Reversible/Quantum Circuits and Ancilla Wires: Early use of
ancillas in Toffoli's paper to implement arbitrary reversible
functions using a fixed number of 3 input gates
\url{https://link.springer.com/content/pdf/10.1007%2F3-540-10003-2_104.pdf}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Pi}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Space Denotational Semantics}
